Fixing Vulnerabilities Potentially Hinders Maintainability

### 2020-09-04 paper/emse20.tex
i think it's ready

\section{Study Implications}\label{sec:implications}
%
Our results show evidence that developers may have to reduce maintainability for the 
sake of security. We argue that developers should be able to patch and produce 
secure code without hindering the maintainability of their projects. But there are 
still concerns that need to be addressed and that this study brings awareness for:
%
\\\textit{\textbf{Tools for Patch Risk Assessment:}}
	Design debt of one guideline can lead
	to severe impacts on the software 
	quality~\cite{10.1145/1985362.1985366}. 
	Thus, tools like Better Code Hub and static analysis (e.g., 
	SonarQube, Codacy, ESLint, Infer, and more) should be leveraged 
	to assess the risk of patching vulnerabilities---alongside pull
	requests/code reviews. Static code analysis may be daunting due 
	to the number of rules and different effects
	on maintainability. BCH claims to use the top-$10$ of the guidelines
	with the highest effect on maintainability. Yet, static analysis 
	can be used to complement the BCH analysis by introducing
	the capability of vulnerability detection and support the prediction/prevention of the risk of hindering maintainability while patching.
%
\\\textit{\textbf{Computer Science Curricula Needs to be Updated:}}
	Computer Science curricula is not yet prepared to properly educate students for maintainable security. 
	    Students should be exposed to this problem to gain experience with it. Curricula should focus on producing 
	    secure and maintainable code and alert to the trade-off between both.
	Universities should also encourage students to use code quality analysis tools such as BCH or similar ones. These tools have a great potential to make
	students aware of maintainability issues and beginner mistakes (e.g.,
	coding practices violation). Thus, students and future developers can 
	put more work into improving their code maintainability and avoiding the risk
	of introducing new vulnerabilities while patching older ones.
%	
\\\textit{\textbf{Secure Programming Languages Wanted:}} Programming Languages 
	should provide new design patterns to easily implement security weaknesses 
	without endangering maintainability.
	Ultimately, new programming languages, both secure and maintainable by design,
	may be designed to help developers be highly productive when writing and
	maintaining secure applications. One example is the need for designing new
	authorization mechanisms since these are one of the most complex security
	features to implement.
% 
% \\\textit{\textbf{Poor Coding Practices Documentation:}}
%   \Rui{too generic?}
% 	Software documentation must be provided to developers with the
% 	best practices to implement secure and maintainable software. Unmaintainable
% 	code is difficult to test, analyze and re-use. Software companies must
% 	do an effort to provide these artifacts to their developers, in order,
% 	to avoid the introduction of new vulnerabilities while patching older ones.

@@

\section{Plan A}

Please, pay more attention to the cases with !.

\begin{itemize}

@@

	\item Implications: Discuss that depending on the project, maybe security 
  is a first class citizen and should be fixed above all. Don't 
  just state that patch risk assessment should take maintainability into account. 
  Saying that security should be a priority requires maybe a user study
  as evidence (check if the literature available is not enough).
  \item Implications: Review the secure programming languages implication. Check 
  if the idea of fully secure exists. The idea should be more secure, not
  fully secure.
  \item [!] Implications: \textit{I am not sure how the computer science curricula got mentioned 
    from a motivation. I don't think vulnerabilities are been introduced, its 
    more that they get exposed. In this case, the implication does not make 
    much sense from a practical point of view.} -> Why not? Shouldn't 
    maintainable security be introduced in the computer science curricula since
    we have evidence that developers might not following good practices while
    patching? If they learn it in college and are aware of it in their jobs
    won't they be better prepared?

@@

\end{itemize}

>>>>

\section{Study Implications}\label{sec:implications}
%
Our results show evidence that developers may have to reduce maintainability for the 
sake of security. We argue that developers should be able to patch and produce 
secure code without hindering the maintainability of their projects. But there are 
still concerns that need to be addressed and that this study brings awareness for:
%
\\\textit{\textbf{Tools for Patch Risk Assessment:}}
	Design debt of one guideline can lead to severe impacts on the 
	software quality~\cite{10.1145/1985362.1985366}. Some software 
	producers consider security as a first class citizen while others 
	do not. As mentioned in previous work, security it is very important and should bee considered as a default feature~\cite{10.1145/2489828.2489830,kurilova2014wyvern,mcgraw2004software}. However, the lack of experts or awareness to the ease of producing vulnerable software leads companies to ship low quality software. Providing automated tools to developers assess the risk of their patches it is important to help companies shipping software of higuer quality. Tools like Better Code Hub and static analysis (e.g., 
	SonarQube, Codacy, ESLint, Infer, and more) can be leveraged 
	to assess the risk of patching vulnerabilities---alongside pull
	requests/code reviews. Static code analysis may be daunting due 
	to the number of rules and different effects
	on maintainability. BCH claims to use the top-$10$ of the guidelines
	with the highest effects on maintainability. Yet, static analysis 
	can be used to complement the BCH analysis by introducing
	the capability of vulnerability detection and support the prediction/prevention of the risk of a patch of hindering maintainability.
%
\\\textit{\textbf{Computer Science Curricula Needs to be Updated:}}
	Computer Science curricula is not yet prepared to properly educate students for maintainable security. 
	    Students should be exposed to this problem to gain experience with it. Curricula should focus on the production of 
	    secure and maintainable code and alert to the trade-off between both. These matters should be discussed and presented to students in software engineering courses.
	Universities should also encourage students to use code quality analysis tools such as BCH or similar ones. These tools have a great potential to make
	students aware of maintainability issues and beginner mistakes (e.g.,
	coding practices violation).
%	
\\\textit{\textbf{More Secure Programming Languages Wanted:}} Programming Languages 
	should provide new design patterns to easily patch security weaknesses 
	without endangering maintainability.
	Ultimately, new programming languages, both secure and maintainable by design, such as Wyvern~\cite{10.1145/2489828.2489830,kurilova2014wyvern}, 
	should be designed to help developers be less vulnerability prone when writing and maintaining secure applications. One example is the need for designing new
	authorization mechanisms since these are one of the most complex security
	features to implement.
% 
% \\\textit{\textbf{Poor Coding Practices Documentation:}}
%   \Rui{too generic?}
% 	Software documentation must be provided to developers with the
% 	best practices to implement secure and maintainable software. Unmaintainable
% 	code is difficult to test, analyze and re-use. Software companies must
% 	do an effort to provide these artifacts to their developers, in order,
% 	to avoid the introduction of new vulnerabilities while patching older ones.

@@

% \section{Plan A}
% Please, pay more attention to the cases with !.

@@

	% \item Implications: Discuss that depending on the project, maybe security
	%   is a first class citizen and should be fixed above all. Don't
	%   just state that patch risk assessment should take maintainability into account.
	%   Saying that security should be a priority requires maybe a user study
	%   as evidence (check if the literature available is not enough).
	%   \item Implications: Review the secure programming languages implication. Check
	%   if the idea of fully secure exists. The idea should be more secure, not
	%   fully secure.
  % \item [!] Implications: \textit{I am not sure how the computer science curricula got mentioned
  %   from a motivation. I don't think vulnerabilities are been introduced, its
  %   more that they get exposed. In this case, the implication does not make
  %   much sense from a practical point of view.} -> Why not? Shouldn't
  %   maintainable security be introduced in the computer science curricula since
  %   we have evidence that developers might not following good practices while
  %   patching? If they learn it in college and are aware of it in their jobs
  %   won't they be better prepared?

@@
